Laplacian envelope

### 2021-11-20 Notes/laplace.tex
start degeneracy section

This leaves two possibilities for the maximum area Markov chain.
Either there is no degeneracy and no shortcuts, which implies the serial topology that we'll discuss in \cref{sec:serialarea}, or there is some degeneracy, which would allow shortcuts provided that they do not bypass an entire degenerate set (see \cref{eq:shortcutarea}).

@@

>>>>

\subsubsection{Degeneracy}\label{sec:degeneracy_area}

\hyperref[sec:areapert]{The previous section} leaves two possibilities for the maximum area Markov chain.
Either there is no degeneracy and no shortcuts, which implies the serial topology that we'll discuss in \cref{sec:serialarea}, or there is some degeneracy, which would allow shortcuts provided that they do not bypass an entire degenerate set (see \cref{eq:shortcutarea}).

@@

We can almost see that degeneracy implies lumpability as follows:
suppose there is a nonzero transition between states \(i\) and \(j\) of type \(\nu\),
Then \(\kktm^\nu_{ij} = 0\) and \cref{eq:areaderivs} becomes
%
\begin{equation}\label{eq:dgn_theta}
\begin{gathered}
  \pdiff{\CL}{\MMdm^\nu_{ij}} =
    r f^\nu \eqm_i \prn{ \brk{\thbm_i - \thbm_j}
     + \prn{c_i + (-1)^\nu + \lambda} \brk{\etwm_i - \etwm_j} } 
    = 0, \\
    \implies \quad
    r f^\nu \eqm_i = 0
    \qquad \text{or} \qquad
    \thbm_i - \thbm_j = -  \prn{c_i + (-1)^\nu + \lambda} \brk{\etwm_i - \etwm_j}. 
\end{gathered}
\end{equation}
%
Therefore, provided that state \(i\) has nonzero equilibrium probability, degeneracy in \(\etw\) implies degeneracy in \(\thb\).

Let \(C_a\) denote the \(a\)'th clump of states that are degenerate in \(\etw\) and \(\thb\), in order of decreasing \(\etw\):
